### 2016-11-08 docs/ms_communitySynchrony.Rmd
fixes labeling in figure 1

---
bibliography: ~/Dropbox/Bibliography/CommunitySynchrony.bib
csl: components/ecology.csl
fontsize: 12pt
geometry: margin=1in
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage{setspace}
- \usepackage{todonotes}
- \doublespacing
- \usepackage{rotating}
- \usepackage{color, soul}
- \usepackage{times} 
- \usepackage[document]{ragged2e}
- \usepackage{titlesec}
- \titleformat{\section}{\Large\sc\centering}{\thesection}{1em}{}
layout: 12pt
linkcolor: black
output:
  pdf_document:
    fig_caption: yes
    keep_tex: no
urlcolor: black
---

@@

While a major step forward, Mutshinda et al.'s (2009) and Thibaut et al.'s (2012) modeling technique does have some limitations.
\textcolor{blue}{First, although both studies quantified the relative importance of environmental stochasticity and interspecific interactions to explain the observed variation of species synchrony, they did not use the model to quantify how much synchrony would change if each factor were removed.
Second, they relied on abundance data that may or may not reliably capture competitive interactions that occur at the individual level.
Third, fluctuations in abundance may mask the mechanisms that underpin species synchrony [@Loreau2008a] and ecosystem stability} [@Loreau2013] \textcolor{blue}{due to legacy effects and ecological drift.
Theory indicates that a focus on the fluctuations of species' per capita growth rates better reveals the mechanisms that ultimately determine species synchrony} [@Loreau2008a],
\textcolor{blue}{which is why we focus per capita growth rates.}

@@

\section{Overview of Our Approach}
\textcolor{blue}{This paper has two related goals.
First, we want to refine previous theory on the drivers of species synchrony} [@Loreau2008a].
\textcolor{blue}{We do not develop new theory, but we do derive new quantitative predictions from previous theory that can be tested with empirical data.
With explicit predictions in hand, we can (i) test the generality of a relatively simple quantitative model and (ii) place our empirical results in a broader theoretical context.
Second, we want to use multispecies population models to run simulation experiments that allow us to quantify the relative influence of theoretical drivers of species synchrony (see Fig. S1 for workflow).
With empirically-based simulations in hand, we can (i) determine the most important drivers of species synchrony in our focal grassland communities and (ii) compare simulation results to theoretical predictions.}

@@

\textcolor{blue}{Our empirical analysis relies on modeling the dynamics of dominant species in five natural semiarid grasslands.
Thus, our focal communities are subsets of the full community.
While this limits our inference to the dynamics of dominant species, the value of our study lies in our ability to explicitly quantify the relative influence of different drivers on species synchrony} [e.g., @Venail2013].

>>>>

---
bibliography: ~/Dropbox/Bibliography/CommunitySynchrony.bib
csl: components/ecology.csl
fontsize: 12pt
geometry: margin=1in
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage{setspace}
- \usepackage{todonotes}
- \doublespacing
- \usepackage{rotating}
- \usepackage{color, soul}
- \usepackage{times} 
- \usepackage[document]{ragged2e}
- \usepackage{titlesec}
- \titleformat{\section}{\large\sc\centering}{\thesection}{1em}{}
layout: 12pt
linkcolor: black
output:
  pdf_document:
    fig_caption: yes
    keep_tex: no
urlcolor: black
---

@@

While a major step forward, Mutshinda et al.'s (2009) and Thibaut et al.'s (2012) modeling technique does have some limitations.
\textcolor{blue}{First, although both studies quantified the relative importance of environmental stochasticity and interspecific interactions to explain the observed variation of species synchrony, they did not use the model to quantify how much synchrony would change if each factor were removed.
Second, they relied on abundance data that may or may not reliably capture competitive interactions that occur at the individual level.
Third, fluctuations in abundance may mask the mechanisms that underpin species synchrony [@Loreau2008a] and ecosystem stability} [@Loreau2013] \textcolor{blue}{due to legacy effects and ecological drift.
Theory indicates that a focus on the fluctuations of species' per capita growth rates better reveals the mechanisms that ultimately determine species synchrony} [@Loreau2008a],
\textcolor{blue}{which is why we focus on per capita growth rates.}

@@

<!--
\section{Overview of Our Approach}
\textcolor{blue}{This paper has two related goals.
First, we want to refine previous theory on the drivers of species synchrony} [@Loreau2008a].
\textcolor{blue}{We do not develop new theory, but we do derive new quantitative predictions from previous theory that can be tested with empirical data.
With explicit predictions in hand, we can (i) test the generality of a relatively simple quantitative model and (ii) place our empirical results in a broader theoretical context.
Second, we want to use multispecies population models to run simulation experiments that allow us to quantify the relative influence of theoretical drivers of species synchrony (see Fig. S1 for workflow).
With empirically-based simulations in hand, we can (i) determine the most important drivers of species synchrony in our focal grassland communities and (ii) compare simulation results to theoretical predictions.}

@@

\textcolor{blue}{Our empirical analysis relies on modeling the dynamics of dominant species in five natural semiarid grasslands.
Thus, our focal communities are subsets of the full community.
While this limits our inference to the dynamics of dominant species, the value of our study lies in our ability to explicitly quantify the relative influence of different drivers on species synchrony} [e.g., @Venail2013].
-->
